The truncated KdV framework for modeling anomalous waves induced by abrupt depth changes

### 2019-07-22 paper2_JNLS/paper.tex
NM

The pivoting motion of the paddle is driven by a 5-phase stepper motor. To generate a randomized incoming wave field, the paddle angle $\phi$ is specified (prescribed) by a precomputed psuedo-random signal	
\begin{align}
\label{PaddleAngle}
& \phi(t) = \phi_0 + \Delta \phi \sum_{n=1}^N a_n \cos(\omega_n t+\delta_n) \, , \\
\label{anEq}
& a_n = \sqrt{\frac{2 \Delta \omega}{\pi^{1/2} \omsig}} \, 
\exp \left( -\frac{(\omega_n - \omavg)^2}{2 \omsig^2} \right) \, ,
\end{align}
(Literal copy and paste) Here, the angular frequencies are evenly spaced $\omega_n = n  \Delta \omega$ with step size $ \Delta \omega = (\omavg+4 \omsig)/N$, where $\omavg$ and $\omsig$ represent the mean and the bandwidth of $\omega$ respectively. We set $\omavg = \omsig = 12.5$ rad/s, corresponding to a peak forcing frequency of 2 Hz and bandwidth of 2 Hz. Importantly, the phases $\delta_n$ are uniformly distributed random variables. We fix $N = 3000$, which sets a fundamental period of $T = 300$ seconds.

@@

	The free surface is illuminated by light-emitting diodes running along the bottom of the tank and then imaged from the sideview with a Nikon D3300 at 60 frames per second. The illumination technique coupled with high pixel count of the camera allows the surface displacement to be resolved with a accuracy better than 1/3 millimeter. Representative free surface measurements are shown in Figs.~\ref{fig2}(a)--(b).

 % Figure 2
%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
\begin{figure}%[!ht]
\begin{center}
\includegraphics[width = 0.85 \linewidth]{Figs/fig2.pdf}
\caption{
(b)--(c) Surface displacement measured at a representative upstream and downstream location. (d)--(e) Corresponding histograms. Reproduced from \cite{bolles2019anomalous}
}
\label{fig2}
\end{center}
\end{figure}
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
 % Data from column 5 in MasterTimeSeries, Delta theta = 1.38 degrees

>>>>

The pivoting motion of the paddle is driven by a 5-phase stepper motor. To generate a randomized incoming wave field, the paddle angle $\phi$ is specified by a precomputed psuedo-random signal
\begin{align}
\label{PaddleAngle}
& \phi(t) = \phi_0 + \Delta \phi \sum_{n=1}^N a_n \cos(\omega_n t+\delta_n) \, , \\
\label{anEq}
& a_n = \sqrt{\frac{2 \Delta \omega}{\pi^{1/2} \omsig}} \, 
\exp \left( -\frac{(\omega_n - \omavg)^2}{2 \omsig^2} \right) \, ,
\end{align}
(Literal copy and paste) Here, the angular frequencies are evenly spaced $\omega_n = n  \Delta \omega$ with step size $ \Delta \omega = (\omavg+4 \omsig)/N$, where $\omavg$ and $\omsig$ represent the mean and the bandwidth of $\omega$ respectively. We set $\omavg = \omsig = 12.5$ rad/s, corresponding to a peak forcing frequency of 2 Hz and bandwidth of 2 Hz. Importantly, the phases $\delta_n$ are uniformly distributed random variables. We fix $N = 3000$, which sets a fundamental period of $T = 300$ seconds.

@@

	The free surface is illuminated by light-emitting diodes running along the bottom of the tank and then imaged from the sideview with a Nikon D3300 at 60 frames per second. The illumination technique coupled with high pixel count of the camera allows surface displacements to be resolved with a accuracy better than 1/3 millimeter. Representative free surface measurements are shown in Figs.~\ref{fig2}(a)--(b) at a position upstream and downstream of the ADC. The corresponding histograms are shown in Figs.~\ref{fig2}(c)--(d).

 % Figure 2
%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
\begin{figure}%[!ht]
\begin{center}
\includegraphics[width = 0.85 \linewidth]{Figs/fig2.pdf}
\caption{
(a)--(b) Surface displacement measured at a representative upstream and downstream location. (c)--(d) Corresponding histograms. Reproduced from \cite{bolles2019anomalous}
}
\label{fig2}
\end{center}
\end{figure}
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
 % Data from column 5 in MasterTimeSeries, Delta theta = 1.38 degrees
